Effects of rotation on the Lyman-$\alpha$ line morphology in distant galaxies

### 2013-04-19 paper/Analisis.tex
New Histograms
Some Comments about the averga number of scatterings

as we think Nscatt is related with the double peacked line and maxima positions

@@

>>>>

Untill know we have focus in how rotation affect the morphology of the lyman alpha line, now we turn to study deeply the posible causes of this effects. As recombination is the main cause of the lyman alpha, it is important to study the relationship between the number of times that a photon is absorbed and re emitted hereafter scatterings with it's shift in the wavelenght. \\

As a first approach we study the number of scatterings of all the photons at different velocites and for both distributions Figure~\ref{fig:Nscatt}. For the central distribution the number of scattering does not change with $V_{max}$ , this implies that..., For the Homogeneous distribution we found that as $V_{max}$ increase the average number of scatterings decrease, it means that rotation..

In order to understand the double peack we make a histogram..

as we think Nscatt is related with the double peacked line and maxima positions.

@@

\begin{figure*}[ht]
    \includegraphics[width=0.45\textwidth]{2dHistogram50Central5t.png}
    \includegraphics[width=0.45\textwidth]{2dHistogram300Central5t.png}
\caption{Nscatt\label{fig:NscattHisto}} 
\end{figure*}
